### 2019-07-10 Writeup/PERT_Paper_Draft3.tex
Save current state

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{accents}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{url}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage{longtable}
\usepackage[noend]{algpseudocode}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\renewcommand{\textfraction}{0.0}
\newcommand{\dst}{\displaystyle}
\newcommand{\minx}{\mbox{\( \dst \min_{x \in X} \)}}
\newcommand{\Efx}{\mbox{\( \dst E f (x, \xi) \)}}
\newcommand{\Efxhat}{\mbox{\( \dst E f (\hat{x}, \xi) \)}}
\newcommand{\hxx}{\mbox{\( \hat{x} \)}}
\newcommand{\bpi}{\bar{\pi}}
\newcommand{\xx}{\mbox{\( x \)}}
\newcommand{\txxi}{\mbox{\(\xi\)}}
\newcommand{\var}{\mbox{var}}
\newcommand{\cF}{{\cal F}}
\newcommand{\cA}{{\cal A}}
\newcommand{\cG}{{\cal G}}
\newcommand{\cN}{{\cal N}}
\newcommand{\cO}{{\cal O}}
\newcommand{\txi}{{\xi}}
\newcommand{\PP}{\mbox{\(SP\)}}
\newcommand{\PPn}{\mbox{\(SP_n\)}}
\newcommand{\PPnx}{\mbox{\(SP_{n_x}\)}}
\newcommand{\noi}{\noindent}
\renewcommand{\ss}{\smallskip}
\newcommand{\ms}{\medskip}
\newcommand{\bs}{\bigskip}
\newcommand{\st}{\mbox{s.t.}}
\newcommand{\wpo}{\mbox{wp1}}
\newcommand{\iid}{\mbox{i.i.d.\ }}
\newcommand{\vsmo}{\vspace*{-0.1in}}
\newcommand{\vsmt}{\vspace*{-0.2in}}
\newcommand{\vso}{\vspace*{0.1in}}
\newcommand{\vst}{\vspace*{0.2in}}
\newcommand{\mc}{\multicolumn}
\newcommand{\cP}{{\cal P}}
\newcommand{\tcb}{\textcolor{blue}}
\newcommand{\underv}{\mbox{$\underbar{$v$}$}}
\newcommand*{\thead}[1]{\multicolumn{1}{c}}
\allowdisplaybreaks

\renewcommand{\P}{{\mathbb P}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\renewcommand{\Re}{{\mathbb R}}
\newcommand{\mbf}{\mathbf}
\renewcommand{\underbar}{\underaccent{\bar}}

@@

		The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \citep{kelley1961criticalpath}; see \citet{soderlund2004building} for an overview. A project is a collection of activities, between which there are precedence relationships due to logical or technological considerations. A precedence relationship is usually reflected as the start time of one activity following the completion of another. Typically, multiple activities can be processed at the same time, and there is no limit on how many activities can be processed simultaneously, as long as the precedence requirements are satisfied. See~\citet{Elmaghraby77} for a detailed treatment of activity networks. In this setting, ``crashing" is an action that consumes a certain amount of one or more resources and shortens the duration of an activity accordingly~\citep{kuhl2008dynamic}. A deterministic optimization model for crashing an activity network was proposed in the 1960s \citep{fulkerson1961network, kelley1961criticalpath}, in which the goal is to complete the project in minimum time by allocating resources under one or more budget constraints.\\

@@

		When the program evaluation and review technique (PERT) was introduced~\citep{malcolm1959application}, activity durations were modeled as independent beta random variables, and the project duration approximated by a normal distribution. Extensions that allow for more general assumptions followed \citep{Elmaghraby77}, and Monte Carlo simulation plays a role in estimating the expected project span, which is difficult to express analytically \citep{burt1971conditional,van1963letter}. Heuristics and simulation-based algorithms have been developed to approximately solve the stochastic project crashing problem \citep{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}. Another approach to handle uncertainty in activity duration is robust optimization, in which the objective is to minimize the worst case project span over a specified uncertainty set. While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \citep{chen2008linear, cohen2007stochastic}. However, once recourse decisions can take general form, the robust model is only tractable with rectangular uncertainty sets

@@

	\section{Problem Formulation} \label{sec:formulation}
		{Nomenclature:}
		\begin{longtable}[H]{ l l l l }
			\multicolumn{4}{l}{\em Indices and index sets} \\
			\(I\) & \(\qquad\) & the set of activities;&\\
			\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i \in I\);&\\
			\(\Omega\) & \(\qquad\) & the index set for disruption scenarios (sample space);&\\
			\(\cA\) &\(\qquad\) & set of arcs, which represents precedence relationships;&\\
			\\
			\multicolumn{4}{l}{\em Parameters} \\
			\(D_{ik}\)& \(\qquad\) & nominal duration between possible start times of activities \(i\) and \(k\), \((i,k) \in \cA\);&\\
			\(e_{ij}\) & \(\qquad\) & effectiveness of crashing option $j \in J_i$ for activity \(i \in I\);&\\
			\(B\) & \(\qquad\) & total budget for crashing options;&\\
			\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j \in J_i\) for activity \(i \in I\);&\\
			\(H^\omega\) &\(\qquad\) & disruption time under scenario \(\omega \in \Omega\);&\\
			\(d_{ik}^\omega\) & \(\qquad\)& increase in duration of \((i,k) \in \cA\) under \(\omega \in \Omega\), if started after the disruption; &\\
			\(p^\omega\) & \(\qquad\) & the probability of scenario \(\omega \in \Omega\);& \\
			\(p^0\) & \(\qquad\) & the probability of no disruption;& \\
			\\
			\multicolumn{4}{l}{\em Decision variables}\\
			\(t_{i}\) & \(\qquad\) & nominal start time of activity \(i \in I\);&\\
			\(x_{ij}\) & \(\qquad\) & crashing of activity \(i \in I\) by option \(j \in J_i\) in the nominal plan; &\\
			\(t_{i}^\omega\) & \(\qquad\) & start time of activity \(i \in I\) under scenario \(\omega \in \Omega\);&\\
			\(x_{ij}^\omega\) & \(\qquad\) & crashing of activity \(i \in I\) by option \(j \in J_i\) under scenario \(\omega \in \Omega\); &\\
			\(G_i^\omega\) & \(\qquad\) & binary indicator whether activity \(i \in I\) starts after disruption under \(\omega \in \Omega\);&\\
			\(z_{ij}^\omega\) & \(\qquad\) & binary term to linearize bilinear term, \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&
		\end{longtable}
		\noi We first review an optimization model for a deterministic crashing problem; see~\citet{fulkerson1961network, kelley1961criticalpath}. A set of activities, \(I\), together with precedence relationships, \(\cA \subseteq I \times I\), form an acyclic activity network \(\mathcal{G} = (I,\cA)\), which represents the project. An arc \((i,k) \in \cA\) indicates that activity \(i\) has to finish before activity \(k\) starts, and its length, \(D_{ik}\), shows that the start time of activity \(i\) has to be at least \(D_{ik} \ge 0\) before the start time of activity \(k\). We create two dummy activities \(S, T \in I\) to represent the start and the termination of the entire project. Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\}\), either directly or by implication, and they both have zero duration.

@@

			\min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\

@@

			& G_i^\omega \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega.

@@

		In this section, we prove that the project crashing optimization problem under a stochastic disruption is NP-hard. The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (\verb|DTCT|) problem. In De et al.~\cite{de1997complexity}, the authors show that an exactly-one-in-three \verb|3SAT| (\verb|EOIT_3SAT|) problem can be transformed to an instance of the \verb|DTCT| decision problem in polynomial time. Since \verb|EOIT_3SAT| is NP-complete (see \cite{Garey1979ComputersAI} for the detailed proof), the authors prove that the \verb|DTCT| decision problem is also NP-complete, and the \verb|DTCT| optimization problem is NP-hard.\\

@@

		Similar to De et al.~\cite{de1997complexity}, we also first introduce the \verb|EOIT_3SAT| problem: let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables. A literal can be either \(u\) or \(\bar{u} = \neg u\) for a \(u \in U\). Let \(C = \{c_1, c_2, \dots, c_m\}\) be a set of clauses, each of which is formed by a disjunction of three literals. The \verb|EOIT_3SAT| problem asks for whether there is a truth assignment for \(U\) such that each clause in \(C\) has exactly one true literal. \\
		Based on the above instance of \verb|EOIT_3SAT|, we formulate an instance of the activity network for the project crashing problem. The activity network consists of three layers of nodes: the first layer contains \(3n\) nodes and represents the truth assignment of each variable; the second layer contains \(3m\) nodes and represents the value of clauses; the third layer contains node \(T\) which represents the end of the project. The first layer has \(n\) components in parallel, each of which corresponds to a variable and contains 3 nodes connected, denoted as \(u_{j1},\ u_{j2}\) and \(u_{j3}\) for the component \(j\), as shown in Figure~\ref{fig:layer1}. Figure~\ref{fig:layer1} also displays how the first layer connects to the third layer. We set the scenario set as a singleton \(\Omega = \{1\}\) and set the disruption time as \(H^1 = 0\) with probability \(p^1 = 1\). We set parameter values associated with the arcs in Figure~\ref{fig:layer1} as:

@@

		We do not allow any activities within the first layer to be crashed, i.e., \(J_{u_{jk}} = \emptyset\), for all \(j = 1,2,\dots, n,\ k = 1,2,3\). With this setup, the length of the critical path for the \(j\)-th component is always \(2\) for all \(j = 1,2,\dots,n\), as it is optimal to have activity \(u_{j1}\) start at time \(0\). However, whether the critical path traverses activities \(u_{j2}\) (top path) or the activity \(u_{j3}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\). If \(G^1_{u_{j1}} = 1\), the \(G\) variables will take value \(1\) for all subsequent nodes. The top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} = 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} + d^1_{u_{j1},u_{j3}} = 2 - 1 = 1\), which makes the top path critical. If \(G^1_{u_{j1}} = 0\), it is optimal to have activity \(u_{j2}\) start before the disruption as well, i.e., \(G^1_{u_{j2}} = 0\). The top path yields a length of \(D_{u_{j1},u_{j2}} = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} = 2\), which makes the bottom path critical. We can consider the value of \(G^1_{u_{j1}}\) as the truth assignment of variable \(u_j\). If the variable \(u_j\) is TRUE, the critical path is the top path; if it is FALSE, the critical path is the bottom path. 

@@

			\includegraphics[width=0.6\textwidth]{layer1}
			\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\) in the first layer of the constructed activity network for \texttt{EOIT\char`_3SAT}.}

@@

		\noi The arcs from activities \(u_{j2}\) and \(u_{j3}\) in Figure~\ref{fig:layer1} point to activities in the second layer. Next, we construct the second layer of activities and the arcs connecting the first layer and the second layer, in a similar manner as Figure 2(b) in~\cite{de1997complexity}. To best illustrate the arc construction, we show an example of a clause, \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\), with two original variables, \(u_j\) and \(u_k\), and one negative complement, \(\bar{u}_{\ell}\). We can consider the activity \(c_{ip}\) corresponding to the truth assignment of the variable \(u_p\), for \(p \in \{j,k,\ell\}\). For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p3}\) with activity \(c_{ip}\), and activity \(u_{p2}\) with activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\). For the negative complement variable \(u_\ell\), we connect activity \(u_{\ell 2}\) with activity \(c_{i \ell}\), and activity \(u_{\ell 3}\) with activities \(c_{iq},\ q \in \{j,k\}\). This example by no means limits the clauses to two variables and one negative complement but aims to showcase the procedure of constructing the network components corresponding to a variable and the negative complement of a variable. From now on we refer to the activities representing variables as \(u\)-activities and those representing clauses as \(c\)-activities.\\

@@

		We let both the nominal duration \(D\) and the disrupted effect \(d\) for the arcs between \(u\)-activities and \(c\)-activities be \(0\). For the arcs between \(c\)-activities and \(T\), we set:
		%The parameters of arcs in Figure~\ref{fig:layer2} are set as:
		& D_{c_{iq},T} = 1 \qquad \quad \;\; d^1_{c_{iq},T} = 0 \;\;\;\quad \forall q \in \{j,k,\ell\}.
		Unlike the \(u\)-activities, each \(c\)-activity can be crashed with a single option with effectiveness \(e_{c_{ip}1} = 1\), \(\forall p \in \{j,k,\ell\}\). The total budget, \(B\), is then set to \(B = 2m\), where \(m\) is the total number of clauses.

@@

			\includegraphics[width=0.5\textwidth]{layer2}
			\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer.}

@@

		\noi For simplicity, the reasoning behind this construction is stated using the example in Figure~\ref{fig:layer2}: for variable \(u_j\), if \(G^1_{u_{j1}} = 1\), the activity \(u_{j4}\) can start at time \(1\), while the earliest time the activity \(u_{j3}\) can start is \(2\). If \(G^1_{u_{j1}} = 0\), the activity \(u_{j3}\) can start at time \(1\), while the earliest time the activity \(u_{j4}\) can start is \(2\). This is the same for variable \(u_k\) but directly opposite for variable \(u_\ell\). The truth assignments indicate which path is critical, which is similar in De et al.~\cite{de1997complexity}, where the truth assignments indicate which crashing option to select for variables nodes. \\

@@

		We can prove the following lemmas. Without loss of generality, a clause can be made of without negative complement of variables. For clarity, Figure~\ref{fig:layer2} equivalent for a clause without negative complement is displayed as Figure~\ref{fig:layer2nonneg}, which is used to illustrate the proofs for Lemma~\ref{lemma:onlyOne} and Lemma~\ref{lemma:iff}.

@@

			\includegraphics[width=0.5\textwidth]{layer2nonneg}

@@

			Without loss of generality, we assume \(q^* = j\).\\

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{scalefnt}
\usepackage{amssymb}
\usepackage{accents}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage[square,sort,comma,numbers]{natbib}
\bibpunct[, ]{(}{)}{,}{a}{}{,}%
\def\bibhang{24pt}%
\def\newblock{\ }%
\def\BIBand{and}
\usepackage{url}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}
\usepackage{algorithm}
\usepackage{longtable}
\usepackage[noend]{algpseudocode}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\renewcommand{\textfraction}{0.0}
\newcommand{\dst}{\displaystyle}
\newcommand{\minx}{\mbox{\( \dst \min_{x \in X} \)}}
\newcommand{\Efx}{\mbox{\( \dst E f (x, \xi) \)}}
\newcommand{\Efxhat}{\mbox{\( \dst E f (\hat{x}, \xi) \)}}
\newcommand{\hxx}{\mbox{\( \hat{x} \)}}
\newcommand{\bpi}{\bar{\pi}}
\newcommand{\xx}{\mbox{\( x \)}}
\newcommand{\txxi}{\mbox{\(\xi\)}}
\newcommand{\var}{\mbox{var}}
\newcommand{\cF}{{\cal F}}
\newcommand{\cA}{{\cal A}}
\newcommand{\cG}{{\cal G}}
\newcommand{\cN}{{\cal N}}
\newcommand{\cQ}{{\cal Q}}
\newcommand{\txi}{{\xi}}
\newcommand{\PP}{\mbox{\(SP\)}}
\newcommand{\PPn}{\mbox{\(SP_n\)}}
\newcommand{\PPnx}{\mbox{\(SP_{n_x}\)}}
\newcommand{\noi}{\noindent}
\renewcommand{\ss}{\smallskip}
\newcommand{\ms}{\medskip}
\newcommand{\bs}{\bigskip}
\newcommand{\st}{\mbox{s.t.}}
\newcommand{\wpo}{\mbox{wp1}}
\newcommand{\iid}{\mbox{i.i.d.\ }}
\newcommand{\vsmo}{\vspace*{-0.1in}}
\newcommand{\vsmt}{\vspace*{-0.2in}}
\newcommand{\vso}{\vspace*{0.1in}}
\newcommand{\vst}{\vspace*{0.2in}}
\newcommand{\mc}{\multicolumn}
\newcommand{\cP}{{\cal P}}
\newcommand{\cH}{{\cal H}}
\newcommand{\thead}{\multicolumn{1}{c |}}
\newcommand{\underv}{\mbox{$\underbar{$v$}$}}
\allowdisplaybreaks

\renewcommand{\P}{{\mathbb P}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\renewcommand{\Re}{{\mathbb R}}
\newcommand{\mbf}{\mathbf}
\renewcommand{\underbar}{\underaccent{\bar}}
\newcommand{\tcr}{\textcolor{red}}
\newcommand{\tcb}{\textcolor{blue}}

@@

	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath}; see \citet{soderlund2004building} for an overview. A project is a collection of activities, between which there are precedence relationships due to logical or technological considerations. A precedence relationship is usually reflected as the start time of one activity following the completion of another. 
	%a required separation time between the start time of two activities. 
	Typically, multiple activities can be processed at the same time, and there is no limit on how many activities can be processed simultaneously, as long as the precedence requirements are satisfied. See~\citet{Elmaghraby77} for a detailed treatment of activity networks. In this setting, ``crashing" is an action that consumes a certain amount of one or more resources and shortens the duration of an activity accordingly~\citep{kuhl2008dynamic}. A deterministic optimization model for crashing an activity network was proposed in the 1960s \citep{fulkerson1961network, kelley1961criticalpath}, in which the goal is to complete the project in minimum time by allocating resources under one or more budget constraints.\\

@@

	When the program evaluation and review technique (PERT) was introduced~\citep{malcolm1959application}, activity durations were modeled as independent beta random variables, and the project duration approximated by a normal distribution. Extensions that allow for more general assumptions followed \citep{Elmaghraby77}, and Monte Carlo simulation plays a role in estimating the expected project span, which is difficult to express analytically \citep{burt1971conditional,van1963letter}.
	Heuristics and simulation-based algorithms have been developed to approximately solve the stochastic project crashing problem \citep{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}. Another approach to handle uncertainty in activity duration is robust optimization, in which the objective is to minimize the worst case project span over a specified uncertainty set. While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \citep{chen2008linear, cohen2007stochastic}. However, once recourse decisions can take general form, the robust model is only tractable with rectangular uncertainty sets

@@

	\section{Problem Formulation} \label{sec:formulation}
	{Nomenclature:}
	%The notation for the model is displayed as follows:
	\begin{longtable}[H]{ l l l l }
		\multicolumn{4}{l}{\em Indices and index sets} \\
		\(I\) & \(\qquad\) & the set of activities;&\\
		\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i \in I\);&\\
		\(\Omega\) & \(\qquad\) & the index set for disruption scenarios (sample space);&\\
		\(\cA\) &\(\qquad\) & set of arcs, which represents precedence relationships;&\\
		\\
		\multicolumn{4}{l}{\em Parameters} \\
		\(D_{ik}\)& \(\qquad\) & nominal duration between possible start times of activities \(i\) and \(k\), \((i,k) \in \cA\);&\\
		\(e_{ij}\) & \(\qquad\) & effectiveness of crashing option $j \in J_i$ for activity \(i \in I\);&\\
		\(B\) & \(\qquad\) & total budget for crashing options;&\\
		\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j \in J_i\) for activity \(i \in I\);&\\
		\(H^\omega\) &\(\qquad\) & disruption time under scenario \(\omega \in \Omega\);&\\
		\(d_{ik}^\omega\) & \(\qquad\)& increase in duration of \((i,k) \in \cA\) under \(\omega \in \Omega\), if started after the disruption; &\\
		\(p^\omega\) & \(\qquad\) & the probability of scenario \(\omega \in \Omega\);& \\
		\(p^0\) & \(\qquad\) & the probability of no disruption;& \\
		\\
		\multicolumn{4}{l}{\em Decision variables}\\
		\(t_{i}\) & \(\qquad\) & nominal start time of activity \(i \in I\);&\\
		\(x_{ij}\) & \(\qquad\) & crashing of activity \(i \in I\) by option \(j \in J_i\) in the nominal plan; &\\
		\(t_{i}^\omega\) & \(\qquad\) & start time of activity \(i \in I\) under scenario \(\omega \in \Omega\);&\\
		\(x_{ij}^\omega\) & \(\qquad\) & crashing of activity \(i \in I\) by option \(j \in J_i\) under scenario \(\omega \in \Omega\); &\\
		\(G_i^\omega\) & \(\qquad\) & binary indicator whether activity \(i \in I\) starts after disruption under \(\omega \in \Omega\);&\\
		\(z_{ij}^\omega\) & \(\qquad\) & binary term to linearize bilinear term, \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&
	\end{longtable}
	\noi We first review an optimization model for a deterministic crashing problem; see~\citet{fulkerson1961network, kelley1961criticalpath}. A set of activities, \(I\), together with precedence relationships, \(\cA \subseteq I \times I\), form an acyclic activity network \(\mathcal{G} = (I,\cA)\), which represents the project. An arc \((i,k) \in \cA\) indicates that activity \(i\) has to finish before activity \(k\) starts, and its length, \(D_{ik}\), shows that the start time of activity \(i\) has to be at least \(D_{ik} \ge 0\) before the start time of activity \(k\). We create two dummy activities \(S, T \in I\) to represent the start and the termination of the entire project. Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\}\), either directly or by implication, and they both have zero duration.

@@

		z^* = \min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\

@@

		& G_i^\omega \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega. \label{cons:Gbounds}

@@

	We show that the optimal project crashing problem under a stochastic disruption is NP-hard even with a single disruption scenario, which occurs with probability one at time zero.
	%The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (\verb|DTCT|) problem. In De et al.~\cite{de1997complexity}, the authors show that an exactly-one-in-three \verb|3SAT| (\verb|EOIT_3SAT|) problem can be transformed to an instance of the \verb|DTCT| decision problem in polynomial time. Since \verb|EOIT_3SAT| is NP-complete (see \cite{Garey1979ComputersAI} for the detailed proof), the authors prove that the \verb|DTCT| decision problem is also NP-complete, and the \verb|DTCT| optimization problem is NP-hard.\\
	%	\newline
	%Similar to De et al.~\cite{de1997complexity}, 
	Our proof relies on a transformation from the exactly-one-in-three \verb|3SAT| (\verb|EOIT_3SAT|) problem: Let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables. A literal can be either \(u\) or \(\bar{u} = \neg u\) for \(u \in U\). Let \(C = \{c_1, c_2, \dots, c_m\}\) be a set of clauses, each of which is formed by a disjunction of three literals, e.g., \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\). The \verb|EOIT_3SAT| problem asks whether there is a truth assignment for each \(u \in U\) such that each clause in \(C\) has exactly one true literal. \citet{de1997complexity} use \verb|EOIT_3SAT| to prove that an activity network problem, in which there are a finite set of alternatives for each activity with different duration and cost, is NP-hard, and we use similar proof constructs. \\

@@

	Starting with an instance of \verb|EOIT_3SAT|, we formulate an activity network using three layers of nodes. The first layer contains \(3n\) nodes and represents the truth assignment of each variable in \verb|EOIT_3SAT|. The second layer contains \(3m\) nodes and represents the value of \verb|EOIT_3SAT|'s clauses. And, the third layer consists of terminal node \(T\), the end of the project. Each of the first layer's \(n\) components corresponds to a variable and contains three nodes, denoted \(u_{j1},\ u_{j2}\), and \(u_{j3}\), which are connected as shown in Figure~\ref{fig:layer1}. The figure also shows how the first layer connects to the third layer. We let \(\Omega = \{1\}\), and \(H^1 = 0\) with probability \(p^1 = 1\). We define the parameter values associated with the arcs in Figure~\ref{fig:layer1} as:
	\begin{subequations}\label{eqn:first_layer}

@@

	No activities in the first layer can be crashed, i.e., 
	\begin{equation}\label{eqn:first_layer_crash}	
	J_{u_{jk}} = \emptyset, \ \mbox{for all} \  j = 1,2,\dots, n,\ k = 1,2,3.
	The start node, $S$, connects to each~$u_{j1}$ with zero duration. It is optimal to start each activity \(u_{j1}\) at time \(0\) because the inclusive inequalities in constraints~\eqref{cons:G1}-\eqref{cons:G2} still allow us to choose \(G^1_{u_{j1}}  \in \{0,1\}\) for each variable in $U$. With this setup, the length of the longer path through the \(j\)-th component is always~\(2\), \(j = 1,2,\dots,n\). Whether the longer path traverses activity~\(u_{j2}\) (top path in Figure~\ref{fig:layer1}) or activity~\(u_{j3}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\). 
	%\tcr{If \(G^1_{u_{j1}} = 1\), the \(G\) variables will take value \(1\) for all subsequent nodes on the path from $u_{j1}$ to $T$.} 
	If \(G^1_{u_{j1}} = 1\) then the top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} = 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} + d^1_{u_{j1},u_{j3}} = 2 - 1 = 1\). If \(G^1_{u_{j1}} = 0\) 
	%\tcr{it is optimal to have activity \(u_{j2}\) start before the disruption as well, i.e., \(G^1_{u_{j2}} = 0\)} 
	then the top path yields a length of \(D_{u_{j1},u_{j2}} = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} = 2\). We can consider the value of \(G^1_{u_{j1}}\) as the truth assignment of variable \(u_j\). If variable \(u_j\) is TRUE, the top path is longer; if it is FALSE the bottom path is longer. 

@@

		\includegraphics[width=0.55\textwidth]{layer1}
		\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\), in the first layer of the activity network for \texttt{EOIT\char`_3SAT}}

@@

	\noi The arcs from activities \(u_{j2}\) and \(u_{j3}\) in Figure~\ref{fig:layer1} point to activities in the second layer, which we now construct, 
	%in a similar manner as Figure 2(b) in~
	again following ideas in~\citet{de1997complexity}. Consider the clause \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\), with literals consisting of two original variables, \(u_j\) and \(u_k\), and one complement, \(\bar{u}_{\ell}\). We consider an activity, \(c_{ip}\), corresponding to the truth assignment of the variable \(u_p\), for \(p \in \{j,k,\ell\}\). For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p3}\) to activity \(c_{ip}\), and we connect activity \(u_{p2}\) to the other two activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\). For the complemented variable~\(\bar{u}_\ell\), we do the opposite, connecting activity \(u_{\ell 2}\) to activity \(c_{i \ell}\), and activity \(u_{\ell 3}\) to activities \(c_{iq},\ q \in \{j,k\}\). This 
	%example by no means limits the clauses to two variables and one negative complement but aims to showcase 
	illustrates the general rule by which a clause with three literals (typically a mix of original and complemented variables) yields the network topology: 
	\begin{subequations}\label{eqn:layer2}
		\begin{eqnarray}	
		&\bullet& \mbox{{\em original variables} result in a connection from $u_{j3}$ to $c_{ij}$ via a single arc and} \nonumber \\
		&& \mbox{a connection from~$u_{j2}$ to the other two $c_j$-activity nodes; and,}  \\
		&\bullet& \mbox{{\em complemented variables} result in the opposite.}
		\end{eqnarray}
	%the procedure of constructing the network components corresponding to a variable and the negative complement of a variable. 
	From now on we refer to the activities representing variables as \(u\)-activities and those representing clauses as \(c\)-activities.\\

@@

	We make the following assignments:
	\begin{subequations}\label{eqn:EOIT_assignments}
		\begin{eqnarray}
		&& D_{u_{jp},c_{ij}}=d^1_{u_{jp},c_{ij}}=0 \qquad \forall i=1,\ldots,m, j=1,\ldots,n, p=2,3: u_j \ \mbox{is in clause} \ c_i \label{eqn:u_c_distance} \\
		&& D_{c_{ij},T}=1 \ \mbox{and} \ d^1_{c_{ij},T}=0 \qquad \forall i=1,\ldots,m, j=1,\ldots,n:  u_j \ \mbox{is in clause} \ c_i  \label{eqn:c_T_distance} \\
		&&e_{c_{ij},1} = 1 \qquad \forall i=1,\ldots,m, j=1,\ldots,n:  u_j \ \mbox{is in clause} \ c_i \label{eqn:e_unit_effectiveness} \\
		&& b_{ij}=1 \qquad \forall i=1,\ldots,m, j=1,\ldots,n:  u_j \ \mbox{is in clause} \ c_i \label{eqn:b_unit_cost} \\
		&& B=2m \label{eqn:budget_is_2m}
		\end{eqnarray}
	The nominal duration and the disrupted duration for the arcs between \(u\)-activities and \(c\)-activities are \(0\) per equation~\eqref{eqn:u_c_distance}. The nominal and disrupted durations for the arcs between the \(c\)-activities and \(T\) are specified in equation~\eqref{eqn:c_T_distance}. Unlike the \(u\)-activities, each \(c\)-activity can be crashed with a single option with unit effectiveness as given in equation~\eqref{eqn:e_unit_effectiveness}. We assign the budget in equation~\eqref{eqn:budget_is_2m}, where \(m\) is the total number of clauses, and assign unit $b_{ij}$ values in equation~\eqref{eqn:b_unit_cost}.

@@

		\includegraphics[width=0.42\textwidth]{layer2}
		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer}

@@

	\noi We illustrate the logic behind this construction using Figure~\ref{fig:layer2}. For variable \(u_j\), if \(G^1_{u_{j1}} = 1\) then the earliest time activity \(u_{j2}\) can start is \(2\), and activity \(u_{j3}\) can start at time \(1\). If \(G^1_{u_{j1}} = 0\) then the earliest time activity \(u_{j3}\) can start is \(2\), and activity \(u_{j2}\) can start at time \(1\). The same holds for variable \(u_k\), and the opposite for variable \(u_\ell\). The truth assignments indicate which path is longer.
	%\tcr{and which crashing option to select for the \tcr{$c$-activity} nodes}. 
	\\

@@

	%	\tcb{We can prove the following lemmas. Without loss of generality, a clause can be made of without negative complement of variables. For clarity, Figure~\ref{fig:layer2} equivalent for a clause without negative complement is displayed as Figure~\ref{fig:layer2nonneg}, which is used to illustrate the proofs for Lemma~\ref{lemma:onlyOne} and Lemma~\ref{lemma:iff}.}
	Next, we establish two lemmas, which relate start times at certain nodes in the activity network corresponding to an instance of \verb|EOIT_3SAT|.

@@

		\includegraphics[width=0.45\textwidth]{layer2nonneg}

@@

		The proof again enumerates eight cases, and we begin with $c_i=u_j \vee u_k \vee u_\ell$; see Figure~\ref{fig:layer2nonneg}. Without loss of generality, we assume \(q^* = j\).\\
		\((\implies)\): In turn we suppose $u_j$ is FALSE or $u_k$ is TRUE or $u_\ell$ is TRUE. 
